HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-10-15 docs/HLL_exp_bad/main.tex
adding perf numbers

SipHash~\cite{AumassonB12} is designed specifically for this use case. It is competitive in speed with non-cryptographic hash functions commonly used in HLL implementations such as MurmurHash3. It has also withstood cryptanalysis well~\cite{DobraunigMS14,XinLSL19}. It has 128-bit outputs that can be truncated to the needs of typical HLL implementations (32 and 64 bits).%and is well supported in libraries such as OpenSSL.

For example, our microbenchmarks created on an Intel i7 CPU show that SipHash-2-4 is as fast as the 128-bit version of MurmurHash3 and only slightly slower than the original 32-bit version.

>>>>

SipHash~\cite{AumassonB12} is designed specifically for this use case. It is competitive in speed with non-cryptographic hash functions commonly used in HLL implementations such as MurmurHash3. It has also withstood cryptanalysis well~\cite{DobraunigMS14,XinLSL19}. It has 128-bit outputs that can be truncated to the needs of typical HLL implementations (32 and 64 bits). %and is well supported in libraries such as OpenSSL.  
Our microbenchmarks created on an Intel i7 CPU show that SipHash-2-4 on 90-byte inputs requires 102ns per evaluation, while the 128-bit version of MurmurHash3 takes 60ns. Meanwhile, HMAC-SHA256 requires 705ns. We obtained similar performance ratios for other input sizes. These together show that SipHash is quite competitive with MurmurHash3.

%is as fast as the 128-bit version of MurmurHash3 and only slightly slower than the original 32-bit version.

%length: 720, time h_mac 705ns, time h_murmur 60ns and time h_sip 102ns
